hbm_paper_results

### 2024-03-08 paper_lbcc_results.Rmd
cleaning up

#get site-level stats
delta_summary.df <- cent_deltas_df_long %>%
  mutate(abs.delta = abs(delta)) %>%
  group_by(study, site) %>%
  summarise(site_mean_abs.delta=mean(abs.delta),
            site_mean_delta=mean(delta),
            site_mean_age=mean(age_days),
            site_mean_age_yrs=mean(age_days)/365.25,
            site_max_abs.delta=max(abs.delta),
            site_n=n())

@@

df_gam_feat_aov.study <- df_gam_feat_aov %>%
  dplyr::filter(term != "Residuals") %>%
  dplyr::mutate(p.val_fdr = p.adjust(p.value, method="fdr", n = length(gam.feat_to_test)), #apply fdr correction across all phenos tested
                  sig_fdr = case_when(p.val_fdr < 0.05 ~ TRUE,
                                      p.val_fdr >= 0.05 ~ FALSE))
df_gam_feat_aov.study %>%
  ggplot() +
  geom_bar(aes(y=sig_fdr))
```

@@

df_gamlss_feat_aov.study %>%
  dplyr::filter(sig_fdr==TRUE)
```
average w/in subject

@@

@@

gam.age.test <- lm(mean_gam_cent ~ site_mean_age, data=gam_centile_site.mean.df2)
summary(gam.age.test)
gam.age.test2 <- lm(mean_gam_cent ~ sex_prop_Female + site_n + site_mean_age, data=gam_centile_site.mean.df2)
summary(gam.age.test2)
```

@@

ComBatLS mean centile ~ age

@@

gamlss.age.test <- lm(mean_gamlss_cent ~ site_mean_age, data=gamlss_centile_site.mean.df2)
summary(gamlss.age.test)
gamlss.age.test2 <- lm(mean_gamlss_cent ~ sex_prop_Female + site_n + site_mean_age, data=gamlss_centile_site.mean.df2)
summary(gamlss.age.test2)
```

>>>>

#get site-level stats
delta_summary.df <- cent_deltas_df_long %>%
  mutate(abs.delta = abs(delta)) %>%
  group_by(study, site) %>%
  summarise(site_mean_abs.delta=mean(abs.delta),
            site_mean_delta=mean(delta),
            site_mean_age=mean(age_days),
            site_mean_age_yrs=mean(age_days)/365.25,
            site_max_abs.delta=max(abs.delta),
            site_n=n()) %>%
  mutate(pheno_cat="all")

# #get w/in cat stats
# delta_summary.cat.df <- cent_deltas_df_long %>%
#   mutate(abs.delta = abs(delta),
#          pheno_cat = case_when(
#     pheno %in% vol_list_global ~ "Global Volume",
#     pheno %in% vol_list_regions ~ "Regional Volume",
#     pheno %in% sa_list ~ "Regional SA",
#     pheno %in% ct_list ~ "Regional CT",
#     TRUE ~ NA_character_)) %>%
#   group_by(study, site, pheno_cat) %>%
#   summarise(site_mean_abs.delta=mean(abs.delta),
#             site_mean_delta=mean(delta),
#             site_mean_age=mean(age_days),
#             site_mean_age_yrs=mean(age_days)/365.25,
#             site_max_abs.delta=max(abs.delta),
#             site_n=n())
# 
# delta_summary.df <- full_join(delta_summary.df, delta_summary.cat.df)

@@

df_gam_feat_aov.study <- df_gam_feat_aov %>%
  dplyr::filter(term != "Residuals") %>%
  dplyr::mutate(p.val_fdr = p.adjust(p.value, method="fdr", n = length(gam.feat_to_test)), #apply fdr correction across all phenos tested
                  sig_fdr = case_when(p.val_fdr < 0.05 ~ TRUE,
                                      p.val_fdr >= 0.05 ~ FALSE))
df_gam_feat_aov.study %>%
  ggplot() +
  geom_bar(aes(y=sig_fdr))

df_gam_feat_aov.study %>%
  dplyr::filter(sig_fdr == TRUE) %>%
  nrow()
```

@@

df_gamlss_feat_aov.study %>%
  dplyr::filter(sig_fdr==TRUE) %>%
  nrow()
```
average w/in subject

@@

```{r}
gam_centile_df.clean_long <- gam_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile")

#overall means
gam_centile_site.mean.df <- gam_centile_df.clean_long %>%
  group_by(study, site) %>%
  summarize(mean_gam_cent=mean(centile)) %>%
  mutate(pheno_cat = "all")

@@

summary(lm(mean_gam_cent ~ site_mean_age, data=gam_centile_site.mean.df2))
summary(lm(mean_gam_cent ~ site_mean_age + sex_prop_Female + site_n, data=gam_centile_site.mean.df2))
```

@@

ComBatLS mean centile ~ age
```{r}
gamlss_centile_df.clean_long <- gamlss_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile")

#overall means
gamlss_centile_site.mean.df <- gamlss_centile_df.clean_long %>%
  group_by(study, site) %>%
  summarize(mean_gamlss_cent=mean(centile)) %>%
  mutate(pheno_cat = "all")

@@

summary(lm(mean_gamlss_cent ~ site_mean_age, data=gamlss_centile_site.mean.df2))
summary(lm(mean_gamlss_cent ~ site_mean_age + sex_prop_Female + site_n, data=gamlss_centile_site.mean.df2))
```
